Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-09-16 prob.tex
prob.tex \subsection{Classical Interval-valued probability measures} Updating...

\begin{definition}~Given an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
\begin{itemize}
\item A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \textrm{probability measure }\pmeas:\events\rightarrow[0,1]\middle|\forall E\in\events.\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $
\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.
\item $\bar{\mu}$ is called \emph{convex} or \emph{2-monotone} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014}.
\end{itemize}
\qed\end{definition}

@@

\begin{thm}{[}Bondareva-Shapley~\cite{Shapley1967,Bondareva1968,Grabisch2016}{]}\label{thm:Bondareva-Shapley}
Let $l$ be the left-end of an interval-valued probability measure~$\bar{\mu}$,
$\bar{\mu}$ has an non-empty core if and only if for any minimal
balanced set~$\left\{ E_{i}\right\} _{i=1}^{N}$, we have $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\gamma_{i}l\left(E_{i}\right)\le1$,
where:
\begin{enumerate}
\item $\left\{ E_{i}\right\} _{i=1}^{N}$ is called balanced set if they
are distinct, $\emptyset\ne E_{i}\subsetneq\Omega$, and there exist
positive coefficient~$\left\{ \gamma_{i}\right\} _{i=1}^{N}$ such
that $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1\textrm{ and }\omega\in E_{i}}^{N}}\gamma_{i}=1$
for all $\omega\in\Omega$.
\item A minimal balanced set is one that includes on other balanced set.
\end{enumerate}
\qed\end{thm}

The Bondareva-Shapley theorem can be used to algorithmically decide
non-empty core because the minimal balanced set can be generated by
an algorithm~\cite{Peleg1965}.

>>>>

\begin{definition}~Given an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
\begin{itemize}
\item A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \textrm{probability measure }\pmeas:\events\rightarrow[0,1]\middle|\forall E\in\events.\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $
\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.
\item $\bar{\mu}$ is called \emph{convex}, \emph{2-monotone}, or\emph{
supermodular} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014,Grabisch2016}.
\end{itemize}
\qed\end{definition}

@@

\begin{thm}[Bondareva-Shapley~\cite{Shapley1967,Bondareva1968,Grabisch2016}]\label{thm:Bondareva-Shapley}
Let $l$ be the left-end of an interval-valued probability measure~$\bar{\mu}$,
$\bar{\mu}$ has a non-empty core if and only if for any minimal balanced
set~$\left\{ E_{i}\right\} _{i=1}^{N}$, we have $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\gamma_{i}l\left(E_{i}\right)\le1$,
where $\left\{ E_{i}\right\} _{i=1}^{N}$ is called minimal balanced
set if they are distinct, $\emptyset\ne E_{i}\subsetneq\Omega$, and
there exist a unique positive coefficient~$\left\{ \gamma_{i}\right\} _{i=1}^{N}$
such that $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1\textrm{ and }\omega\in E_{i}}^{N}}\gamma_{i}=1$
for all $\omega\in\Omega$.

\qed\end{thm}

The Bondareva-Shapley theorem can be used to algorithmically decide
non-empty core because the minimal balanced set can be generated by
an algorithm~\cite{Peleg1965}. However, the number of minimal balanced
sets grows very rapidly with the size of $\Omega$, $\left|\Omega\right|$,
so that we have only verified every interval-valued probability measure
has a non-empty core when $\left|\Omega\right|\le5$ so far.
